Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-08-21 tex/robustness.tex
update

\begin{figure}[ht]
  \caption{Estimated Coefficients for  Policy Variables: Sensitivity Analysis \label{fig:whisker}}\bigskip
  \begin{minipage}{\linewidth}
    \centering
   {\textbf{(A)  masks for employees}}\\
    \medskip
    \begin{tabular}{cc}  
 $\quad$  (i) baseline timing$^\dagger$ &$\quad$ (ii) alternative timing$^\ddagger$\\ 
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-whisker-14}
      &
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-whisker-9} 
    \end{tabular}
  \end{minipage} \\\smallskip
    \begin{minipage}{\linewidth}
    \centering 
     {\textbf{(B)  closed K-12 Schools}}\\
    \medskip
    \begin{tabular}{cc}  
 $\quad$  (i) baseline timing$^\dagger$ &$\quad$ (ii) alternative timing$^\ddagger$\\ 
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pk12-whisker-14}
      &
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pk12-whisker-9}
          \end{tabular}
  \end{minipage}  
    \begin{flushleft}
      \footnotesize
      $^\dagger$The times from exposure to case confirmation and death reporting  are assumed to be 14 and 21 days, respectively. $^\ddagger$The times from exposure to case confirmation and death reporting  are assumed to be 9 and 24 days, respectively. 
    \end{flushleft}
\end{figure}

   \addtocounter{figure}{-1}
\begin{figure}[ht]
  \caption{Estimated Coefficients for Policy Variables:  Sensitivity Analysis (cont.) \label{fig:whisker-2}}\bigskip
  \begin{minipage}{\linewidth}
    \centering
   {\textbf{(C)  stay-at-home orders}}\\
    \medskip
    \begin{tabular}{cc}  
 $\quad$  (i) baseline timing$^\dagger$ &$\quad$ (ii) alternative timing$^\ddagger$\\ 
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pshelter-whisker-14}
      &
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pshelter-whisker-9} 
    \end{tabular}
  \end{minipage} \\ \smallskip
    \begin{minipage}{\linewidth}
    \centering 
     {\textbf{(D)  Average of stay-at-home, closed movie theaters, closed restaurants, and closed  businesses}}\\
    \medskip
    \begin{tabular}{cc}  
 $\quad$  (i) baseline timing$^\dagger$ &$\quad$ (ii) alternative timing$^\ddagger$\\ 
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pindex-whisker-14}
      &
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pindex-whisker-9}
          \end{tabular}
  \end{minipage}   
    \begin{flushleft}
      \footnotesize
      $^\dagger$The times from exposure to case confirmation and death reporting  are assumed to be 14 and 21 days, respectively. $^\ddagger$The times from exposure to case confirmation and death reporting  are assumed to be 9 and 24 days, respectively. 
    \end{flushleft}
\end{figure}

@@

   \end{tabular}
   }
   \begin{flushleft}
     \scriptsize Dependent variable is the weekly growth rate of
     confirmed cases (in the left panel) or deaths (in the right
     panel) as defined in equation (\ref{eq:y}).        The covariates
     include lagged policy variables, which are
     constructed as 7 day moving averages between $t$ to $t-7$ of
     corresponding daily measures.  The row
     ``$\sum_j \mathrm{Policies}_j$'' reports the sum of six policy
     coefficients.  Standard errors are clustered at the state level.
   \end{flushleft}
 \end{minipage}
\end{table}
\end{landscape}
}

>>>>

\begin{figure}[ht]
  \caption{Estimated Coefficients for  Policy Variables: Sensitivity Analysis \label{fig:whisker}}\bigskip
  \begin{minipage}{\linewidth}
    \centering
   {\textbf{(A)  masks for employees}}\\
    \medskip
    \begin{tabular}{cc}  
 $\quad$  (i) baseline timing$^\dagger$ &$\quad$ (ii) alternative timing$^\ddagger$\\ 
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-whisker-14}
      &
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pmaskbus-whisker-7} 
    \end{tabular}
  \end{minipage} \\\smallskip
    \begin{minipage}{\linewidth}
    \centering 
     {\textbf{(B)  closed K-12 Schools}}\\
    \medskip
    \begin{tabular}{cc}  
 $\quad$  (i) baseline timing$^\dagger$ &$\quad$ (ii) alternative timing$^\ddagger$\\ 
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pk12-whisker-14}
      &
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pk12-whisker-7}
          \end{tabular}
  \end{minipage}  
    \begin{flushleft}
      \footnotesize
      $^\dagger$The times from exposure to case confirmation and death reporting  are assumed to be 14 and 21 days, respectively. $^\ddagger$The times from exposure to case confirmation and death reporting  are assumed to be 9 and 24 days, respectively. 
    \end{flushleft}
\end{figure}

   \addtocounter{figure}{-1}
\begin{figure}[ht]
  \caption{Estimated Coefficients for Policy Variables:  Sensitivity Analysis (cont.) \label{fig:whisker-2}}\bigskip
  \begin{minipage}{\linewidth}
    \centering
   {\textbf{(C)  stay-at-home orders}}\\
    \medskip
    \begin{tabular}{cc}  
 $\quad$  (i) baseline timing$^\dagger$ &$\quad$ (ii) alternative timing$^\ddagger$\\ 
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pshelter-whisker-14}
      &
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pshelter-whisker-7} 
    \end{tabular}
  \end{minipage} \\ \smallskip
    \begin{minipage}{\linewidth}
    \centering 
     {\textbf{(D)  Average of stay-at-home, closed movie theaters, closed restaurants, and closed  businesses}}\\
    \medskip
    \begin{tabular}{cc}  
 $\quad$  (i) baseline timing$^\dagger$ &$\quad$ (ii) alternative timing$^\ddagger$\\ 
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pindex-whisker-14}
      &
      \includegraphics[width=0.5\textwidth]{tables_and_figures/pindex-whisker-7}
          \end{tabular}
  \end{minipage}   
    \begin{flushleft}
      \footnotesize
      $^\dagger$The times from exposure to case confirmation and death reporting  are assumed to be 14 and 21 days, respectively. $^\ddagger$The times from exposure to case confirmation and death reporting  are assumed to be 9 and 24 days, respectively. 
    \end{flushleft}
\end{figure}

@@

   \end{tabular}
   }
   \begin{flushleft}
     \scriptsize   All specifications include weekly dummies and state fixed effects. Dependent variable is the weekly growth rate of
     confirmed cases (in the left panel) or deaths (in the right
     panel) as defined in equation (\ref{eq:y}).   Columns (1) and (3) report the standard fixed effects estimator  while Columns (2) and (4) report the fixed effects estimator with bias corrections.    Standard errors are computed by multiplier bootstrap clustered at the state level.

   \end{flushleft}
 \end{minipage}
\end{table}
\end{landscape}
}
